Figures

### 2021-02-16 inst/manuscript/figures.Rmd
Additional accuracy metrics added to SI.

# zone maps
zone_grps <- list("aoi" = list(1:3, 4:9, c(10:11, 13, 14, 16), c(12, 15)),
                  "aez" = list(1, 2:4, 5, 6:7))
aoi_zones <- aois %>% 
  mutate(zone = case_when(
    aois %in% zone_grps$aoi[[1]] ~ "Zone 1", 
    aois %in% zone_grps$aoi[[2]] ~ "Zone 2", 
    aois %in% zone_grps$aoi[[3]] ~ "Zone 3", 
    aois %in% zone_grps$aoi[[4]] ~ "Zone 4")
  ) %>%
  group_by(zone) %>% 
  summarize(area = sum(area))

@@

rf_tbl <- tibble(x = 1, y = 10, dat = list(rf_tabs))

# segmentation accuracy
segreports <-  lapply(accuracy_reports$zones$aoi, function(x) x$seg)
segreports[[length(segreports) + 1]] <- accuracy_reports$ghana$seg
seg_tabs <- lapply(1:5, function(x) {  # x <- 1
  m <- segreports[[x]]
  d <- data.frame(m, check.names = FALSE)
  rbind(d, rep("", ncol(d)))
}) %>% do.call(rbind, .)
colnames(seg_tabs) <- colnames(rfreports$North)
seg_tbl <- tibble(x = 1, y = 10, dat = list(seg_tabs))

# Assemble plots with maps
# Table theme
tt <- ttheme_gtminimal(
  base_size = 4.5, 
  padding = unit(c(0.2, 0.2), "char"),
  core = list(fg_params = list(hjust = 1, x = 1))
)

m <- ggplot(aoi_zones) + geom_sf(lwd = 0.1) + 
  geom_sf_text(data = st_centroid(aoi_zones), aes(label = zone), size = 2) + 
  theme_void() + theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))

t1 <- ggplot() + 
  geom_table(data = rf_tbl, aes(x = x, y = y, label = dat), table.theme = tt) + 
  ggtitle("Per-pixel classification") + 
  theme_void() + 
  theme(plot.title = element_text(hjust = 0.5, vjust = 1, size = 6))
t2 <- ggplot() + 
  geom_table(data = seg_tbl, aes(x = x, y = y, label = dat), table.theme = tt) + 
  ggtitle("Segmentation") +
  theme_void() + 
  theme(plot.margin = unit(c(0,0,0,0), "cm"), 
        plot.title = element_text(hjust = 0.5, vjust = 1, size = 6))

# gp <- cowplot::plot_grid(t1, m, t2, nrow = 1, align = "hv", 
#                          # rel_widths = c(0.2, 0.4, 0.5, 0.4, 0.2),
#                          rel_widths = c(1, 1, 0.8),
#                          # rel_heights = c(0.5, 1.5, 0.5),
#                          scale = c(0.25, 0.95, 0.25),
#                          label_size = 5, 
#                          label_x = 0.25, 
#                          labels = c("Per-pixel classification", "",
#                                     "Segmentation"))
gp <- t1 + m + t2
ggsave(gp, filename = pth("figures/figure7.png"), width = 7.25, height = 2.35, 
       units = "in", dpi = 300)
```

@@

### Figure S9: Segmentation statistics (grid scale)

>>>>

@@

# rf_tbl <- tibble(x = 0, y = 10, dat = list(rf_tabs))

# segmentation accuracy
segreports <-  lapply(accuracy_reports$zones$aoi, function(x) x$seg)
segreports[[length(segreports) + 1]] <- accuracy_reports$ghana$seg
seg_tabs <- lapply(1:5, function(x) {  # x <- 1
  m <- segreports[[x]]
  d <- data.frame(m, check.names = FALSE)
  rbind(d, rep("", ncol(d)))
}) %>% do.call(rbind, .)
seg_tabs <- cbind(zvec, seg_tabs)
colnames(seg_tabs) <- c("", colnames(rfreports$North))#rep("", ncol(seg_tabs))
# seg_tbl <- tibble(x = 0, y = 10, dat = list(seg_tabs))

all_tbl <- tibble(x = 0, y = 10, dat = list(rbind(rf_tabs, seg_tabs)))

# Assemble plots with maps
# Table theme
tt <- ttheme_gtminimal(
  base_size = 10, 
  padding = unit(c(0.7, 0.3), "char"),
  core = list(fg_params = list(hjust = 1, x = 1)), 
  colhead = list(fg_params = list(hjust = 1, x = 1))
)

t1 <- ggplot(data.frame(x = c(0, 10), y = c(0, 10))) + 
  geom_point(aes(x = x, y = y), shape = "") +  
  geom_table(data = all_tbl, aes(x = x, y = y, label = dat), table.theme = tt) + 
  # ggtitle("Per-pixel classification") + 
  annotate(geom = "text", x = -0.2, y = 7, #y = 1, yend = 5, 
           label = "Per-pixel classification", angle = 90) +
  annotate(geom = "text", x = -0.2, y = 2.5, label = "Segmentation", 
           angle = 90, hjust = 1) +
  annotate(geom = "segment", x = -0.2, xend = 10, y = 9.77, yend = 9.77) + 
  annotate(geom = "segment", x = -0.2, xend = 10, y = 10.02, yend = 10.02) + 
  annotate(geom = "segment", x = -0.2, xend = 10, y = 4.7, yend = 4.7, 
           size = 0.3) + 
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5, vjust = 1, size = 6), 
        plot.margin = unit(c(0, 0, 0, 0), "cm"))

# gp <- t1 + m
ggsave(t1, filename = pth("figures/figure7.png"), width = 7, height = 7.9, 
       units = "in", dpi = 300)
```

@@

### Figure S9: AOI Zones

```{r, eval=FALSE}
# zone maps
zone_grps <- list("aoi" = list(1:3, 4:9, c(10:11, 13, 14, 16), c(12, 15)),
                  "aez" = list(1, 2:4, 5, 6:7))
aoi_zones <- aois %>% 
  mutate(zone = case_when(
    aois %in% zone_grps$aoi[[1]] ~ "Zone 1", 
    aois %in% zone_grps$aoi[[2]] ~ "Zone 2", 
    aois %in% zone_grps$aoi[[3]] ~ "Zone 3", 
    aois %in% zone_grps$aoi[[4]] ~ "Zone 4")
  ) %>%
  group_by(zone) %>% 
  summarize(area = sum(area))

rmapshaper::ms_simplify(aez) %>% plot()
aez %>% st_buffer(dist = 0.01) %>% st_union(by_feature = TRUE) %>% 
  st_buffer(dist = -0.01) %>% 
  mutate(zone = case_when(
    ID %in% zone_grps$aez[[1]] ~ "Zone 1", 
    ID %in% zone_grps$aez[[2]] ~ "Zone 2", 
    ID %in% zone_grps$aez[[3]] ~ "Zone 3", 
    ID %in% zone_grps$aez[[4]] ~ "Zone 4")
  ) %>%
  group_by(zone) %>% 
  summarize(area = sum(AREA)) %>% plot()

aez_zones <- rmapshaper::ms_simplify(aez, keep = 1) %>% 
  mutate(zone = case_when(
    ID %in% zone_grps$aez[[1]] ~ "Zone 1", 
    ID %in% zone_grps$aez[[2]] ~ "Zone 2", 
    ID %in% zone_grps$aez[[3]] ~ "Zone 3", 
    ID %in% zone_grps$aez[[4]] ~ "Zone 4")
  ) %>%
  group_by(zone) %>% 
  summarize(area = sum(AREA)) 
# plot(aez_zones["area"])
# plot(aez["AREA"])

m <- ggplot(aois) + geom_sf(lwd = 0.1) +
  geom_sf(data = aoi_zones, lwd = 0.5, fill = "transparent") + 
  geom_sf_text(data = st_centroid(aoi_zones), aes(label = zone), size = 4) + 
  theme_void() + theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))

m2 <- ggplot(aez %>% filter(ID != 8)) + geom_sf(lwd = 0.1) +
  geom_sf(data = aez_zones, lwd = 0.5, fill = "transparent") + 
  geom_sf_text(data = st_centroid(aez_zones), aes(label = zone), size = 4) + 
  theme_void() + theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))

ggsave(m + m2 + plot_annotation(tag_levels = 'A'), 
       filename = pth("figures/si_aoi_zones.png"), width = 3.5 * 2, 
       height = 4.5, units = "in", dpi = 300)
```

### Figure S10: AEZ accuracies

Grouped by four zones, calculated for per-pixel classifications only.

# RF accuracy
rfreports <- lapply(accuracy_reports$zones$aez, function(x) x$rf)
rf_tabs <- lapply(1:4, function(i) {  # i <- 2
  m <- rfreports[[i]]
  d <- data.frame(m, check.names = FALSE)
  rbind(d, rep("", ncol(d)))
}) %>% do.call(rbind, .)
zvec <- rep("", nrow(rf_tabs))
znames <- paste(paste("Zone", 1:4), "  ")
zvec[c(3, seq(8, length(zvec), by = 5))] <- znames
rf_tabs <- cbind(zvec, rf_tabs)
colnames(rf_tabs) <- c("", colnames(rfreports$Coast_Sav))

all_tbl <- tibble(x = 0, y = 10, dat = list(rf_tabs))

# Assemble plots with maps
# Table theme
tt <- ttheme_gtminimal(
  base_size = 10, 
  padding = unit(c(0.7, 0.3), "char"),
  core = list(fg_params = list(hjust = 1, x = 1)), 
  colhead = list(fg_params = list(hjust = 1, x = 1))
)

t1 <- ggplot(data.frame(x = c(0, 10), y = c(0, 10))) + 
  geom_point(aes(x = x, y = y), shape = "") +  
  geom_table(data = all_tbl, aes(x = x, y = y, label = dat), table.theme = tt) + 
  annotate(geom = "segment", x = 0, xend = 10, y = 9.5, yend = 9.5) + 
  annotate(geom = "segment", x = 0, xend = 10, y = 10.01, yend = 10.01) + 
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5, vjust = 1, size = 6), 
        plot.margin = unit(c(0, 0, 0, 0), "cm"))

ggsave(t1, filename = pth("figures/si_aez_accuracies.png"), width = 7, 
       height = 3.5, units = "in", dpi = 300)
```

### Figure S11: Segmentation statistics (grid scale)
